Union and Intersection Contracts Are Hard, Actually

### 2021-09-28 paper.tex
Implement corrections for camera-ready version

\lstset{
  language={nickel},
  basicstyle=\small\ttfamily, % Global Code Style
  captionpos=b, % Position of the Caption (t for top, b for bottom)
  extendedchars=true, % Allows 256 instead of 128 ASCII characters
  tabsize=2, % number of spaces indented when discovering a tab
  columns=fixed, % make all characters equal width
  keepspaces=true, % does not ignore spaces to fit width, convert tabs to spaces
  showstringspaces=false, % lets spaces in strings appear as real spaces
  breaklines=true, % wrap lines if they don't fit
  frame=trbl, % draw a frame at the top, right, left and bottom of the listing
    frameround=tttt, % make the frame round at all four corners
  framesep=4pt, % quarter circle size of the round corners
  numbers=none, % show line numbers at the left
  % numberstyle=\tiny\ttfamily, % style of the line numbers
  escapeinside={(*@}{@*)} % escape sequence to insert latex
  % commentstyle=\color{dark-grey}, % style of comments
  % keywordstyle=[1]\color{blue-portage}, % style of keywords
  % keywordstyle=[2]\color{orange-vivid-tangerine}, % style of keywords
  % keywordstyle=[3]\color{blue-portage}, % style of keywords
  % keywordstyle=[4]\color{green-pea}, % style of keywords
  % keywordstyle=[5]\color{pink-froly}, % style of keywords
  % stringstyle=\color{blue-marguerite}, % style of strings
}

\lstset{
  escapeinside={(*@}{@*)}, % escape sequence to insert latex
  numbers=none, % for the camera-ready version: numbers overlap with margins
  % Avoid overlap with margins
  framexleftmargin = -2pt,
  framexrightmargin = -2pt,
  framextopmargin = -2pt,
  framexbottommargin = -2pt
}

@@

\subsection{Contributions}
Our contributions are as follows
\begin{itemize}
\item We describe the fundamental difficulties caused by presence of
  union and intersection contracts in a language, which are kept
  implicit in the literature (Section~\ref{sec:issues-sem})
\item We survey the various trade-offs which appear in implemented
  languages and in the academic literature to work around these difficulties
  (Section~\ref{sec:issues-literature})
\end{itemize}

\section{A Typology Of Language Features}
\label{sec:feat-lang}

@@

\subsection{Intersection With User-Defined Contracts}
\label{sec:flat-and-inter}

>>>>

\lstset{
  language={nickel},
  basicstyle=\small\ttfamily, % Global Code Style
  captionpos=b, % Position of the Caption (t for top, b for bottom)
  extendedchars=true, % Allows 256 instead of 128 ASCII characters
  tabsize=2, % number of spaces indented when discovering a tab
  columns=fixed, % make all characters equal width
  keepspaces=true, % does not ignore spaces to fit width, convert tabs to spaces
  showstringspaces=false, % lets spaces in strings appear as real spaces
  breaklines=true, % wrap lines if they don't fit
  % frame=trbl, % draw a frame at the top, right, left and bottom of the listing
    % frameround=tttt, % make the frame round at all four corners
  % framesep=4pt, % quarter circle size of the round corners
  numbers=none, % show line numbers at the left
  % numberstyle=\tiny\ttfamily, % style of the line numbers
  escapeinside={(*@}{@*)} % escape sequence to insert latex
  % commentstyle=\color{dark-grey}, % style of comments
  % keywordstyle=[1]\color{blue-portage}, % style of keywords
  % keywordstyle=[2]\color{orange-vivid-tangerine}, % style of keywords
  % keywordstyle=[3]\color{blue-portage}, % style of keywords
  % keywordstyle=[4]\color{green-pea}, % style of keywords
  % keywordstyle=[5]\color{pink-froly}, % style of keywords
  % stringstyle=\color{blue-marguerite}, % style of strings
}

\lstset{
  escapeinside={(*@}{@*)}, % escape sequence to insert latex
  numbers=none, % for the camera-ready version: numbers overlap with margins
  % Avoid overlap with margins
  % framexleftmargin = -2pt,
  % framexrightmargin = -2pt,
  % framextopmargin = -2pt,
  % framexbottommargin = -2pt
}

@@

\subsection{Contributions}
Our contributions are as follows
\begin{itemize}
\item We describe the fundamental difficulties caused by pre-sence of
  union and intersection contracts in a language, which are kept
  implicit in the literature (Section~\ref{sec:issues-sem})
\item We survey the various trade-offs which appear in implemented
  languages and in the academic literature to work around these difficulties
  (Section~\ref{sec:issues-literature})
\end{itemize}

\section{A Typology of Language Features}
\label{sec:feat-lang}

@@

\subsection{Intersection with User-Defined Contracts}
\label{sec:flat-and-inter}
